\subsection{What is Qubit?}
Qubit is the fundamental unit of quantum information. Compaired to the classical bit, qubit requires complex vector space where qubits becomes complex vector and quantum gates becomes matrices.
\bea
\alpha |0> + \beta |k>
\eea
\subsection{How is qubit different from classical bit?}
Qubit is the fundamental unit of quantum information. Compaired to the classical bit, qubit requires complex vector space where qubits becomes complex vector and quantum gates becomes matrices.
\bea
\begin{bmatrix}
a & b\\
c & d\\
\end{bmatrix}
\eea
\subsection{What is superposition of qubits?}

\subsection{How is two qubits system represented?}

\subsection{What are the postulates of quantum mechanics?}

\subsection{What is bloch sphere?}

\subsection{What is coherence?}

\subsection{What is decoherence?}

\subsection{what are pure and mixed states?}

\subsection{What is entanglement?}

\subsection{What is superdense coding?}

\subsection{What is teleportation?}

\subsection{What is bell state?}

\subsection{What is Heisenberg Uncertainty?}

\subsection{What is measurement?}

\subsection{What is quantum parallelism?}

\subsection{It is possible to construct quantum parallel of classical gates?}

\subsection{What is the difference between separable and entangled state?}

\subsection{What happens to the quantum state after a measurement?}

\subsection{What is local(relative) and global phase of qubit?}

\subsection{What is Born rule?(Qiskit1.1)}

\subsection{What is conservation of certainty?(Qiskit1.4)}

\subsection{What is quantum simulation?}
